---
title: "Mantel Test"
author: "Vergara, Diana Carolina"
date: "21/8/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
##Mantel Test

#With ape

> library(ape)
> mantel.test
function (m1, m2, nperm = 999, graph = FALSE, alternative = "two.sided", 
    ...) 

> mantel.test("ZzHW61iR3OWxp0bXH9o05Q_nexus.txt", "Phylo_FULL_Muricea_nexus.txt", nperm = 9999, graph = TRUE)
Error in `diag<-`(`*tmp*`, value = 0) : 
  only matrix diagonals can be replaced
  
```{r}
library(ape)
mantel.test("ZzHW61iR3OWxp0bXH9o05Q_nexus.txt", "Phylo_FULL_Muricea_nexus.txt", nperm = 9999, graph = TRUE)
```

########################

#With ade4
https://stat.ethz.ch/pipermail/r-help/2006-October/114933.html
#If the dissimilarity matrices are full, square, symmetric matrices, then you can use:

#mantel.rtest(as.dist(your_mat1), as.dist(your_mat2))

```{r}
mantel.rtest(as.dist(your_mat1), as.dist(your_mat2))
```

> library(ade4)
> mantel.rtest(Phylo_FULL_Muricea_nexus.txt, ZzHW61iR3OWxp0bXH9o05Q_nexus.txt, nrepet = 9999)
> mantel.rtest("Phylo_FULL_Muricea_nexus.txt", "ZzHW61iR3OWxp0bXH9o05Q_nexus.txt", nrepet = 9999)

> mantel.rtest(as.dist("Phylo_FULL_Muricea_nexus.txt"), as.dist("ZzHW61iR3OWxp0bXH9o05Q_nexus.txt"), nrepet = 9999)
Error in if (is.euclid(m1) & is.euclid(m2)) { : 
  missing value where TRUE/FALSE needed
In addition: Warning messages:
1: In storage.mode(m) <- "numeric" : NAs introduced by coercion
2: In storage.mode(m) <- "numeric" : NAs introduced by coercion

dis.muricea<-dist("Phylo_FULL_Muricea_nexus.txt")
Warning message:
In dist("Phylo_FULL_Muricea_nexus.txt") : NAs introduced by coercion


############


#PhyloMantel
In evolqg: Tools for Evolutionary Quantitative Genetics
Description
Performs a matrix correlation with significance given by a phylogenetic Mantel Test. Pairs of rowns and columns are permuted with probability proportional to their phylogenetic distance.

Usage
1
2
3
PhyloMantel(tree, matrix.1, matrix.2, ..., permutations = 1000,
  ComparisonFunc = function(x, y) cor(x[lower.tri(x)], y[lower.tri(y)]),
  k = 1)
  
data(dentus)
data(dentus.tree)
tree = dentus.tree
cor.matrices = dlply(dentus, .(species), function(x) cor(x[-5]))
comparisons = MatrixCor(cor.matrices)

sp.means = dlply(dentus, .(species), function(x) colMeans(x[-5]))
mh.dist = MultiMahalanobis(means = sp.means, cov.matrix = PhyloW(dentus.tree, cor.matrices)$'6')
PhyloMantel(dentus.tree, comparisons, mh.dist, k = 10000)

#similar to MantelCor for large k:
## Not run: 
PhyloMantel(dentus.tree, comparisons, mh.dist, k = 10000)
MantelCor(comparisons, mh.dist)

```{r}
data(dentus)
data(dentus.tree)
tree = dentus.tree
cor.matrices = dlply(dentus, .(species), function(x) cor(x[-5]))
comparisons = MatrixCor(cor.matrices)

sp.means = dlply(dentus, .(species), function(x) colMeans(x[-5]))
mh.dist = MultiMahalanobis(means = sp.means, cov.matrix = PhyloW(dentus.tree, cor.matrices)$'6')
PhyloMantel(dentus.tree, comparisons, mh.dist, k = 10000)

#similar to MantelCor for large k:
## Not run: 
PhyloMantel(dentus.tree, comparisons, mh.dist, k = 10000)
MantelCor(comparisons, mh.dist)
```

